### 2020-06-29 docs/LaTex/Paper.tex
Minor fixes in the first docs draft

\begin{itemize}
  \item A rotary potentiometer does work well enough as a proof of concept, but would have been more appropriate to have the expected linear potentiometer to try its sensibility, which is a good point in order to measure such little variations as produced in the stem diameter in a tree.
  \item The fact that the Raspberry Pi HAT uses a single channel chip (SX1276) has two important implications:
    \begin{itemize}
      \item In a first place, as indicated in its corresponding section, these kind of gateways are LoRaWAN compatible but not compliant. So it would be desirable to replace this HAT by another one, or simple to acquire a proper gateway for a production environment.
      \item Nodes cannot comunicate simultaneously with the gateway because it is listening only one channel, so this is causing a time gap in data acquisition as can be seen in the picture \ref{fig:times_gap}
      \begin{figure}[ht]
        \centering
        \includegraphics[width=.9\textwidth]{../pictures/Grafana_times_gap.png}
        \caption{Little gap between times caused by the single channel chip.}
        \label{fig:times_gap}
      \end{figure}
    \end{itemize}
    \item Maybe the developed GUI could have handle also the context data plots, however this project couldn't have covered in anyway this development with the available time, so this is not considered as part of the project because Grafana is complete enough to this task for now and perhaps for ever due it is extremely powerful handling databases.
    \item For a production environment it seems clear that arduino devices should be encapsulated and the sensor (potentiometer) part must be improved; however this is not hard because of the wide offer for cases and power supply systems, this would lead a very compact device which could be also improved adding more sensor due versatility of CayenneLPP encoding standard which allows to send multiple measurements of different sensors. 
    \item Finally this project is a good candidate to replace expensive commercial and proprietary systems; so it likely keeps developing, depending on the needs of the researchers.
\end{itemize}

>>>>

\begin{itemize}
  \item A rotary potentiometer does work well enough as a proof of concept, but would have been more appropriate to have the expected linear potentiometer to try its sensibility, which is a good point in order to measure such little variations as produced in the stem diameter in a tree.
  \item The fact that the Raspberry Pi HAT uses a single channel chip (SX1276) has two important implications:
    \begin{itemize}
      \item In a first place, as indicated in its corresponding section, these kind of gateways are LoRaWAN compatible but not compliant. So it would be desirable to replace this HAT by another one, or simple to acquire a proper gateway for a production environment.
      \item Secondly, Nodes cannot comunicate simultaneously with the gateway because it is listening only one channel, so this is causing a time gap in data acquisition as can be seen in the picture \ref{fig:times_gap}
      \begin{figure}[ht]
        \centering
        \includegraphics[width=.9\textwidth]{../pictures/Grafana_times_gap.png}
        \caption{Little gap between times caused by the single channel chip.}
        \label{fig:times_gap}
      \end{figure}
    \end{itemize}
    \item Maybe the developed GUI could have handle also the context data plots, however this project couldn't have covered in anyway this development with the available time, so this is not considered as part of the project because Grafana is complete enough to this task for now and perhaps for ever due it is extremely powerful handling databases.
    \item For a production environment it seems clear that arduino devices should be encapsulated and the sensor (potentiometer) part must be improved; however this is not hard because of the wide offer for cases and power supply systems, this would lead a very compact device which could be also improved adding more sensor due versatility of CayenneLPP encoding standard which allows to send multiple measurements of different sensors. 
    \item Finally this project is a good candidate to replace expensive commercial and proprietary systems; so it likely keeps developing, depending on the needs of the researchers.
\end{itemize}
